Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-04-19 docs/00-manuscripts/ieee/ieee-manuscript.tex

% RQ4: Which features are most important for the models and how can these be interpreted in an ecological context?
Features along the red-edge wavelength region were most important for models to achieve good predictions.
With respect to dedicated vegetation indices, the "Vogelmann" index with all of its versions was seen as the most important index for the tested SVM algorithm.

>>>>

% RQ4: Which features are most important for the models and how can these be interpreted in an ecological context?
Features along the red-edge wavelength region were most important for models to achieve good predictions.
With respect to dedicated vegetation indices, the "Vogelmann" index with all of its derivatives was seen as the most important index for the best performing SVM model.
This matches well with the actual purpose of these indices: 
These were invented to detect defoliation on sugar marple trees (\textit{Acer saccharum Marsh.}) caused by pear thrips (\textit{Taeniothrips inconsequens Uzel}) in 1988 \cite{vogelmann1993}.
